Intersection of non-matching grids of different dimensions

### 2016-09-25 paper_intersections.tex
Almost finished 23d algo
- seems that it could be done this way and description is almost finished
- rather try to simplify whole thing modifying original approach

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is a polygon with 7 vertices at maximum. The sides of the polygon
are coincident with either sides of $S_3$ or with faces of the $S_4$. So a vertex of the polygon
can arise from intersection of a side with a face or an edge with $S_3$ or from a vertex of $S_3$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.

Computation of the intersection polygon consists of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every of its sides. There are 0,1, or 2 intersection points
on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
through all the sides and appending the points into $I$ provides us with incomplete intersection polygon but in the correct order.
\notePE{Comment on process point (Algorithm \ref{algo:process_point}), face relation indicator, I would move description of face table here, since I looked at algorithm1 here, from it skipped to process point and I got lost..}

\notePE{If IP lies on an edge(s) of $S_4$, we create a mark so we exclude the edges from further computation in Algorithm \ref{algo:collect_23_ip_edges}.}

\notePE{In process point, we set for all the face of the vertex, if we coming through the vertex in or out the $S_4$. I understand that the condition on line 10 means, that we do not overwrite info if there is another IP on that face..}

\notePE{I corrected the algorithm references. Please check, it is ok now..}

Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
with faces of $S_4$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

@@

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  $I =\emptyset$\tcp*{Intersection polygon.}
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
  $V =\emptyset$\tcp*{$S_4$ vertex intersections.}
  \For{side $s$ of $S_3$}{ 
    \nllabel{line:1_3}
    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
    process point($L[0]$, 0)\; 
    process point($L[-1]$, 1)
    \notePE{Isn't it clearer to write the two process point lines into cycle over L?}
  }
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
  \notePE{I am not sure if I understand the notation '($[-1]$)', can be explained?
The last line then checks if first and last IPs, if they are not duplicates..??}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}
\end{algorithm}

\begin{algorithm}
  \caption{process point( $p$, $i$ )}

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{intersection point $p$, face relation indicator $i$}
  \KwOut{update of $I$ and $F$}
  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
  \If{ $p$ is not vertex of $S_3$}{    
  \notePE{I am missing the check whether IP is vertex of $S_3$ as referred in text.
  So what if it is a vertex?}\;
    set $j$ to index of $p$ in $I$\;
    \lIf{ $p$ is on face $f$}{ F[i,f]=j}
    \uElseIf{ $p$ is on edge $e$}{
        F[i, $e$]=j
    }
    \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
        F[i, $v$] =j
   }
  }    
  \label{algo:process_point}
\end{algorithm}

\begin{algorithm}
  \label{algo:collect_23_ip_edges}
  \caption{2d-3d intersection, points in triangle interior}

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  \For{edge $e$ of $S_4$}{
    $p$ = intersection($e, S_3$)\;
    \uIf{ $p$ is on boundary of $S_3$}{

    }
    \Else{
        append $p$ to $I$\;
        set $j$ to index of $p$ in $I$\;
        \uIf{ $p$ is inside of $e$}{ 
            sort faces $f_0$, $f_1$ coincident with $e$\;
            F[0, $f_0$]=j\;
            F[1, $f_1$]=j
        } %else
        \Else($p$ on the vertex $v$ of $S_4$){       
        append $j$ to $V$
        \For{face $f$ coincident with $v$}{
            \lIf{ $F[i,f]==-1$}{F[i,f]=j}
        }
        mark all edges of $S_4$ coincident with $v$
        }
     }   
  }
\end{algorithm}

@@

  \SetKw{To}{To}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $K$ in correct order}  
  \If{\abs{V} = 3}{

  }
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \For{ $f$ is face of $S_4$}{
    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
    \notePE{condition should be $F[0,f] \ne F[1,f]$ ? I don't understand: successor indices should be switched?
    This way there would be same two indices..}
  }
  $i=0$

  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
  \label{algo:order_23}
\end{algorithm}

>>>>

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
are coincident with either sides of $S_3$ or with faces of the $S_4$. Thus each vertex of the polygon
can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
Computation of the intersection polygon consists of three parts: calculation of IPs on the $S_3$ boundary (Algorithm \ref{algo:colect_23_ip_triangle}),
calculation of IPs in the interior of $S_3$ (Algorithm \ref{algo:collect_23_ip_edges}), and finalize the correct order of IPs (Algorithm \ref{algo:order_23}).

\begin{algorithm}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}

  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs on sorted output data}  
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}

  \For{side $i$ of $S_3$}{ 
    $L$ = intersection($i, S_4$)\;
    \For{ $p \in L$, $p \ne I[-1]$ }{append $p$ to $I$}    
    \lIf{$\abs{L}=2$}{
        append $0,0$ to $s$
    } \lElse {
        append $1$ to $s$
    }
  }
  \nllabel{line:ip_first_vtx_duplicate}
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}

  $l=0$
  \For{$p \in I$}{
    set $j$ to index of $p$ in $I$\;
    \If{ $p$ is on boundary of $S_4$}{
      $x$ is vertex,edge, or face on which $p$ lies\; 
      \For{ $i=0,\dots, s[j]$}{
        $F[l, x]=j$\;
        $l=1-l$ \tcp*{switch from input to output and vice versa}
      }  
    }
  }  
\end{algorithm}

In Algorithm \ref{algo:colect_23_ip_triangle}, we first compute IPs
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. Every IP that is not same as the previous IP 
(occures at vertices of $S_3$) is appended to $I$. The IPs are added in the order around $S_3$ which match the orientation of the intersection polygon.
The array $s$ indicates IPs that comes from side touching $S_4$ at its edge or vertex. 
At line \ref{line:ip_first_vtx_duplicate}, we remove posible dupicate IP for the first vertex.
Then we pass through $I$ and denote to the table $F$ at which IP ($j$) the polygon's boundary switchs from the $S_4$ boundary to the $S_3$ boundary
($l=0$) and vice versa ($l=1$). The table $F$ contains the entry ($l=1$) and leave ($l=0$) IP for every geometrical object (vertex, edge, or  face) 
$x$ on the boundary. In particular the touching IPs appear in both directions. The result of Algorithm \ref{algo:colect_23_ip_triangle} is incomplete 
list $I$ of IPs lying on the $S_3$ boundary and the table $F$ stores relation of the objects on the $S_4$ boundary to the IPs on the $S_3$ boundary.

\begin{algorithm}  
  \caption{2d-3d intersection, points in triangle interior}
  \label{algo:collect_23_ip_edges}

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partialy filled $F$}
  \KwOut{all IPs in $I$, complete $F$}

  \nllabel{line:12edges}
  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)} 
  \For{unmarked edge $e$ of $S_4$}{
    \uIf{ $L[e]$ is inside of $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = edge faces($e$)
    } 
    \Else($p$ on the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = vertex faces($v$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
    }    
    \uIf{ $L[e]$ is on boundary of $S_3$ }{
         \uIf{ $L[e]$ is inside of $e$}{ 
             get $i$ such that $F[i,e] = k$, $k\ne -1$
         }
         \Else($p$ on the vertex $v$ of $S_4$){ 
             get $i$ such that $F[i,v] = k$, $k\ne -1$          
         }         
         $F[1-i, f_{1-i}] = k$\;
    }
    \Else{
         append $L[e]$ to $I$\;
         set $j$ to index of $L[e]$ in $I$\;
         F[0, $f_0$]=j\;
         F[1, $f_1$]=j\;
         mark all edges coincident with $L[e]$
    }   
  }  
\end{algorithm}

\begin{algorithm}
  \caption{2d-3d intersection, vertex faces}  
  \label{algo:vertex_faces}

  \SetKw{return}{return}
  \DontPrintSemicolon
  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
  \KwOut{faces $S_4$ intersected by the plane of $S_3$}
  $e_0,\ e_1,\ e_2$ edges coincident with $v$\;
  $s[i] = L[e_i]$, for $i=0,1,2$\;
  \nllabel{line:two_degenerated}
  \uIf{$s$ have 1 non-degenerate edge $e$}{
    \return pair of degenerate edges sorted according to \edgefaces($e$)    
  }
  \nllabel{line:one_degenerated}
  \uElseIf{ $s$ have 1 degenerate edge $e$}{
    $f$ is face opposite to $e$first of faces coincident with $e$\;
    $g$ is non-degenerate edge coincident with $f$\;
    \return edge faces($g$)
  }
  \nllabel{line:different_sign}
  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{
    \return edge faces($e$)\;
  }
  \nllabel{line:same_signs}
  \Else($s$ have all signs same){
    \return anything\;
  }  
\end{algorithm}

Algorithm \ref{algo:collect_23_ip_edges} use the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produce IPs from interior of $S_3$ and possibly those already computed IPs with special position on vertex or edge of $S_4$. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ apear in the same order on the intersection polygon when the 
IP of $e$ have negative sign (see Figure \ref{fig:plucker_products}). The function "edge faces" used on line \ref{line:edge_faces} and later on 
use the sign of the intersection to return the pair of faces in the correct order. 
Similarly the function "vertex faces" (Algorithm \ref{algo:vertex_faces}) described latter on
returns pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.

\subsubsection{Vertex Faces Algorithm}
This function get an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
The functin returns pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
Basic idea is to use the signs of IPs of the three edges coincident with $v$. 
Possible cases are:
\begin{itemize}
 \item {\bf All IPs have same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
 in the vertex $v$, the polygon ddegenerates to the single IP $p$, no connectionn information from table $F$ necessary.
 \item {\bf Single IP have sign oposite to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single $IP$ with different sign. 
 The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function edge faces.
 \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
 The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$.

 The edge $e$ lies in the the singel edge
 \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
 We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces fro edge $e$.
\end{itemize}

Either all signs are equal ($S_3$ touching $S_4$) wee , or
a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the

and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
with faces of $S_4$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

@@

@@

  \SetKw{To}{to}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $K$ in correct order}  
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \lFor{ $f$ is face of $S_4$}{$P[ F[1,f] ] = F[0, f]$}
  $i=0$\;  
  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
  \label{algo:order_23}
\end{algorithm}
